Presentation Title

### 2017-03-15 presentation.tex
Presentation of current work

\begin{frame}{TrustChain}
  \begin{itemize}
    \item Everyone has their own chain
    \item Transactions are on arbitrary data $m$
    \item Transactions make the chains intertwined
    \item No consensus (my thesis)
  \end{itemize}
\end{frame}

@@

\subsection{Consensus Protocol Overview}
\begin{frame}{Consensus Protocol Overview}
  \begin{enumerate}
    \item $N$ lucky nodes are selected at random to act as promoters.
    \item Every node sends CP blocks to promoters.
    \item Promoters run a BFT (Byzantine Fault Tolerant) consensus algorithm to
      agree on a set of CP blocks---$\mathcal{C}_r$.
    \item Disseminate $\mathcal{C}_r$.
    \item Any node can verify that their transaction is in consensus.
    \item Repeat for next round.
  \end{enumerate}
\end{frame}

@@

@@

\begin{frame}{Blocks}
\begin{block}{Block Title}
You can also highlight sections of your presentation in a block, with it's own title
\end{block}
\begin{theorem}
There are separate environments for theorems, examples, definitions and proofs.
\end{theorem}
\begin{example}
Here is an example of an example block.
\end{example}
\end{frame}

% Placing a * after \section means it will not show in the
% outline or table of contents.
\section*{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}

  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}

% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{For Further Reading}

  \begin{thebibliography}{10}

  \beamertemplatebookbibitems
  % Start with overview books.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.

  \beamertemplatearticlebibitems
  % Followed by interesting articles. Keep the list short.

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

\end{document}

>>>>

\begin{frame}{TrustChain}
  \begin{itemize}
    \item Everyone has their own chain
    \item Transactions are on arbitrary data $m$
    \item Transactions make the chains intertwined
    \item Transactions are irrefutable due to hash pointers
    \item No consensus (my thesis)
  \end{itemize}
\end{frame}

@@

\subsection{Protocol Overview}
\begin{frame}{Protocol Overview}
  \begin{enumerate}
    \item $n$ lucky nodes are selected at random to act as promoters.
    \item Promoters run a BFT (Byzantine Fault Tolerant) consensus algorithm to
      agree on a set of CP blocks.
    \item Disseminate the consensus result (the CP blocks).
    \item Repeat for next round.
    \item Any interested node can validate that their transaction.
  \end{enumerate}
\end{frame}

@@

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-1}
  \centering
  \caption{We start in the state where $\mathcal{C}_{r - 1}$ has just been agreed but
    not yet propagated.}
  \end{figure}

@@

\begin{frame}{Promoter Registration}

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-2}
  \centering
  \caption{Nodes receive consensus result and set promoters indicator $p$, then
    send the new CP blocks to promoters of round $r$.}
  \end{figure}

\begin{frame}{Promoter Registration}

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-3}
  \centering
  \caption{Transactions carry on as usual in round $r$. Note that our CP blocks
    (round $r - 1$) has not reached consensus yet.}
  \end{figure}

\begin{frame}{Promoter Registration}

  \begin{figure}[h]
  \includegraphics[width=0.7\textwidth]{figures/trustchain-4}
  \centering
  \caption{CP blocks at round $r-1$ should be in $\mathcal{C}_r$. If we're
    lucky: $\texttt{h}(k_i || c_{i,j}) < T$, then we're responsible for
    consensus of round $r + 1$.}
  \end{figure}

\subsection{Consensus}
\begin{frame}{Consensus}
  \begin{enumerate}
    \item Nodes send CP blocks to the promoters.
    \item The promoters' identities are encoded in the consensus result.
    \item Promoters run the some asynchronous BFT consensus algorithm to agree on
      a set of CP blocks---$\mathcal{C}_r$.
    \item $n = 3t + 1$ is the optimal for BFT consensus.
    \item $\mathcal{C}_r$ and the signatures are disseminated.
    \item Nodes create new CP blocks when they receive $t + 1$ good signatures and
      $\mathcal{C}_r$.
  \end{enumerate}

  \begin{theorem}
    Assuming the promoters satisfy $n = 3t + 1$. The promoter registration and
    the consensus protocol satisfied agreement, total order and liveness.
  \end{theorem}
\end{frame}

\subsection{Validation}

\begin{frame}{Validation}
Assume node $u$ is aware of all the past consensus results $\mathcal{C}_r$.
Suppose $u$ wish to validate $t_{i,j}$. It performs the following.

\begin{enumerate}
\item Determine the pair $t_{i', j'}$.
\item Find the agreed enclosure for $t_{i,j}$ and $t_{i', j'}$ from
  $\mathcal{C}_r$, otherwise return ``unknown''.
%\item Find the smallest $c_{i', b}$ such that $b > j'$ is in consensus.
\item Query $i$ and $i'$ for the agreed pieces and ensure hash pointers are
  correct. Otherwise return ``unknown''.
\item Check that $t_{i,j}$ and $t_{i', j'}$ are in the agreed pieces and are
  created correctly using \texttt{newtx}. Otherwise return ``invalid''.
\item Check the checkpoints $c_{i, k}$ and $c_{i', k'}$ that immediately follow
  $t_{i,j}$ and $t_{i', j'}$ are in the agreed pieces and are created in the
  same round, i.e. $\texttt{round}(c_{i, k}) = \texttt{round}(c_{i', k'})$.
  Otherwise return ``invalid''.
\item Return ``valid''.
\end{enumerate}
\end{frame}

\begin{frame}{Validation}
  In essence, given a TX, ask the receiver to proof that it has a set of
  transactions that produces some CP block, the CP block should be in the
  consensus result and the pair of the TX should be in that set.

  \begin{theorem}
    If at least one party of every transaction is honest, then forking and other
    forms of tampering is guaranteed to be detected if the malicious party is
    alive.
  \end{theorem}
\end{frame}

\subsection{Implementation}
\begin{frame}{Implementation}
  \begin{itemize}
    \item Currently on going---using Python and Twisted
    \item Completed BFT consensus algorithm
    \item Completed local TrustChain
    \item Next step is networked TrustChain and validation protocol
  \end{itemize}
\end{frame}
\end{document}
